### 2020-08-21 latex/vlp.tex
Edited the description of the VLP and added the figure

The variable length pendulum (VLP) is modelled as a point with mass \(m\)
connected to a pivot by a massless rod of varying length. Label
\(q \in \mathbb{S}^1\) as the angle from the vertical line to the rod. In a
realizable VLP, the rod  has length \(l\) which varies between some minimum
length \(\underline{l} \geq 0\) and some maximum length 
\(\overline{l} > \underline{l}\). The configuration of the VLP is the vector
\(\mathbf{q} := (q,l) \in \mathbb{S}^1 \times [\underline{l},\overline{l}]\).

>>>>

The variable length pendulum (VLP) is modelled as a point with mass \(m\)
connected to a pivot by a massless rod of varying length \(l\) and angle 
\(q \in \mathbb{S}^1\) from the vertical, as is seen in Figure
\ref{fig:vlp_model}. 
In a realistic VLP, the rod length \(l\) varies between some minimum
length \(\underline{l} \geq 0\) and some maximum length 
\(\overline{l} > \underline{l}\). The configuration of the VLP is the vector
\(\mathbf{q} := (q,l) \in \mathbb{S}^1 \times [\underline{l},\overline{l}]\).

\begin{figure}
   \centering
   \includestandalone[width=0.4\textwidth]{images/vlp_model}
   \caption{The variable length pendulum with a mass at the
   tip.}\label{fig:vlp_model}
\end{figure}
